An Autonomous and Decentralized Data Marketplace for Trusted Machine Economy $^{\dagger}$

### 2019-12-31 paper.tex
Simplify payoff diagram name scheme

\begin{figure}[H] \centering \includegraphics[width=3.3 in]{payoff_pic} \caption{Payoff Function}
    \label{fig:payoff_pic} \end{figure}

With proper tuning factor, we can derive payoff function which is similar to Figure \ref{fig:payoff_pic}. The red dot in this figure indicates the data quality that data provider would most likely provide, since the data provider can achieve maximum payoff at that point. Namely, the red dot is the Nash Equilibrium of this game theory model. Both scales of x-axis and y-axis have been normalized. X-axis is normalized into a range between 0 to 100 which can reflect customer satisfaction of data buyers, y-axis is normalized into a range between -1 and 1.

Figure \ref{fig:payoff_pic} illustrates the market mechanism of the subscription trading policy we used under the decentralized data marketplace. First, data providers have weak motivation to operate their sensor in low accuracy, since the incentive of low quality data is much less than moderate quality data. Second, the great deficit at high accuracy is mostly derived by the rapid increasing of maintenance cost. Thus, if the maintenance fee to achieve decent data quality is under a fair price range, then data provider will automatically provide data with high enough data quality under our assumptions.

>>>>

\begin{figure}[H] \centering \includegraphics[width=3.3 in]{payoff} \caption{Payoff Function}
    \label{fig:payoff} \end{figure}

With proper tuning factor, we can derive payoff function which is similar to Figure \ref{fig:payoff}. The red dot in this figure indicates the data quality that data provider would most likely provide, since the data provider can achieve maximum payoff at that point. Namely, the red dot is the Nash Equilibrium of this game theory model. Both scales of x-axis and y-axis have been normalized. X-axis is normalized into a range between 0 to 100 which can reflect customer satisfaction of data buyers, y-axis is normalized into a range between -1 and 1.

Figure \ref{fig:payoff} illustrates the market mechanism of the subscription trading policy we used under the decentralized data marketplace. First, data providers have weak motivation to operate their sensor in low accuracy, since the incentive of low quality data is much less than moderate quality data. Second, the great deficit at high accuracy is mostly derived by the rapid increasing of maintenance cost. Thus, if the maintenance fee to achieve decent data quality is under a fair price range, then data provider will automatically provide data with high enough data quality under our assumptions.
